---
title       : Shiny App for Air Pollutant Data
subtitle    : The Developing Data Product project of coursera
author      : Cheng-Hsien Tang
job         : 5-page slides for the project
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The dataset

1. Fine particulate matter (PM2.5) ambient air pollutant sample dataset from Environmental Protection Agency
2. Being used in the Exploratory Data Analysis Course of Coursera
3. Made some pre-processing to increase the speed of app

--- .class #id 

## The column type
```{r echo = FALSE}
nei1 <- read.csv("summaryPM25_1999.csv")
head(nei1)
```


1. fips: A five-digit number (represented as a string) indicating the U.S. county  dataset from Environmental Protection Agency. Reference site: http://www.epa.gov/enviro/html/codes/state.html.
2. Emissions: The emissions of different types in ton.
3. type: The type of source. (point, non-point, on-road, or non-road)
4. After the input of variable, press the process button to calculate the results

--- .class #id 



## The result

```{r echo = FALSE}
nei1 <- read.csv("summaryPM25_1999.csv")
nei2 <- read.csv("summaryPM25_2002.csv")
nei3 <- read.csv("summaryPM25_2005.csv")


nei_array <- array(dim=c(3,2)) 
nei_array[1,1] <- c("1999") 
nei_array[2,1] <- c("2002") 
nei_array[3,1] <- c("2005") 
nei_array[1,2] <- colSums (subset(nei1, nei1[,1] == 24510 & nei1[,3] == "POINT", select = c("Emissions")), na.rm = T, dims = 1) 
nei_array[2,2] <- colSums (subset(nei2, nei2[,1] == 24510 & nei2[,3] == "POINT", select = c("Emissions")), na.rm = T, dims = 1) 
nei_array[3,2] <- colSums (subset(nei3, nei3[,1] == 24510 & nei3[,3] == "POINT", select = c("Emissions")), na.rm = T, dims = 1) 
plot(nei_array[,1], as.numeric(nei_array[,2]), ylab='Total Emission (ton)', xlab='',type='b') 


```

1. After the calculation. There is a plot that show the emission change during time.


--- .class #id 

## Reference

1. Shiny app: http://sealer22.shinyapps.io/DevelopDataProduct
2. Source code: https://github.com/sealer22/DevelopDataProduct
3. Document: https://github.com/sealer22/DevelopDataProduct/blob/master/How_to_use_the_shiny_app.pdf



